\section{Periodic Scheduling}
Periodic scheduling is always preemptive.
\begin{center}
	{\renewcommand{\arraystretch}{2}
	\begin{tabular}{|c|c|c|}
		\hline
							& Deadline = Period	& Deadline $\leq$ Period	\tabularnewline\hline
		Static Priority		& Rate Monotonic	& Deadline Monotonic		\tabularnewline\hline
		Dynamic Priority	& EDF				& EDF*						\tabularnewline\hline
	\end{tabular}}
\end{center}

\subsection{Definitions}
\begin{itemize}
	\item $\Gamma = \set{\tau_1, \tau_2, \dots \tau_n}$	is set of periodic tasks.
	\item $\tau_{i,j}$ is the $j$-th instance of task $\tau_i$.
	\item $a_{i,j}, r_{i,j}, d_{i,j}, s_{i,j}, f_{i,j}$ are the same as for aperiodic tasks.
	\item $\Phi_i$ is the phase of task $i$ (release time of the first instance).
	\item $D_i$ is the relative deadline of task $i$.
	\item $T_i$ is the period of the task (time between 2 releases).
\end{itemize}

The following hypotheses are assumed
\begin{itemize}
	\item $r_{i,j} = \Phi_i + (j - 1) T_i$
	\item $C_i$ is constant.
	\item $d_{i,j} = \Phi_i + (j - 1) T_i + D_i$
	\item The tasks are independent
\end{itemize}

\subsection{Rate Monotonic}
Always schedule the task that has the shortest period.
Sufficient (but not necessary) schedulability test:
\begin{equation*}
	\sum_{i = 1}^n \frac{C_i}{T_i} \leq n \left( 2^{\frac{1}{n}} - 1 \right)
\end{equation*}

\subsection{Deadline Monotonic}
Always schedule the task that has the shortest relative deadline.
Sufficient (but not necessary) schedulability test:
\begin{equation*}
	\sum_{i = 1}^n \frac{C_i}{D_i} \leq n \left( 2^{\frac{1}{n}} - 1 \right)
\end{equation*}

\subsection{Necessary and sufficient schedulability test}
We define the interference $I_i$ for task $i$ as
\begin{equation*}
	I_i(t) = \sum_{j = 1}^{i - 1} \ceil{\frac{t}{T_j}} C_j
\end{equation*}
where the tasks are ordered such that $m < n \iff D_m < D_n$

\subsubsection{Algorithm}
The tasks are ordered as described above.
\begin{lstlisting}[escapeinside={(*}{*)}]
foreach ((*$\tau_i$*) (*$\in$*) (*$\Gamma$*)) {
	I = 0;
	do {
		R = I + (*$C_i$*);
		if (R > (*$D_i$*)) return false; // unschedulable
		I = (*$\sum\limits_{j = 1}^{i - 1} \ceil{\frac{\mathrm{R}}{T_j}} C_j$*);
	} while (I + (*$C_i$*) > R);
}
return true;
\end{lstlisting}
The final values \texttt{R} are the longest response times.

\subsection{EDF}
Always schedule the task with the earliest deadline.
Schedulable with EDF iff $\sum\limits_{i = 1}^{n} \frac{C_i}{T_i} = U \leq 1$.
